The Astropy Project

### 2017-10-04 main.tex
new features

\begin{itemize}
\item ASCII : fast reader/writer (1.0), HTML tables
\item FITS: lazy loading, command-line scripts (fitsheader, fitsinfo)
\end{itemize}

>>>>

\begin{description}

    \item[ASCII: fast reader/writer (v1.0)]

		The \package{astropy.io.ascii} module now includes a significantly faster
		Cython/C engine for reading and writing ASCII files. This is available
		for the following formats: basic, commented\_header, csv, no\_header,
		rdb, and tab.  On average the new engine is about 4 to 5 times faster
		than the corresponding pure-Python implementation, and is often
		comparable to the speed of the pandas ASCII file interface. The fast
		reader has parallel processing option that allows harnessing multiple
		cores for input parsing to achieve even greater speed gains.

		By default, read() and write() will attempt to use the fast C engine when
		dealing with compatible formats. Certain features of the full read / write
		interface are not available in the fast version, in which case the
		pure-Python version will automatically be used.

    \item[ASCII: HTML tables]
		TODO.

	\item [FITS: command-line scripts (fitsheader, fitsinfo)]
		TODO.

	\item [FITS: lazy loading (v1.3)]
		The \package{astropy.io.fits} sub-package now supports \emph{lazy
		loading}, where all HDUs are not loaded until they are requested (or
		the file is closed). This should provide substantial speedups for
		situations using the convenience functions (e.g., \texttt{getheader()}
		or \texttt{getdata()}) to get HDU’s that are near the front of a file
		with many HDU’s.

	\item [Misc: YAML serialization (v1.3)]
		The new \astropy{astropy.io.misc.yaml} module
		allows converting astropy objects into a standard YAML format.
